---
title: "MacroEconomics_1"
author: "Mathias Flinta"
date: "30/10/2019"
output: html_document
---

```{r}
library(expm)
library(igraph)
library(networkD3)
#install.packages("https://github.com/S120/PKSFC/raw/master/PKSFC_1.5.tar.gz", repos = NULL) 
library(PKSFC)
```

# Solow

## Baseline
```{r}
solow<-sfc.model("Solow.txt",modelName="solow") # this reads the model from text file 
solow<-sfc.check(solow,fill=T) # this checks whether system of equations is complete 
data<-simulate(solow, maxIter=200) # this simulates the model for 200 iterations
y_model1 = data$baseline[,"y"] # this extracts a variable of interest (y in this case) 
k_model1 = data$baseline[,"k"] # this extracts k from the model

plot(y_model1, t="l", ylab="output per worker", xlab="")

plot(k_model1, t="l", ylab = "capital per worker", xlab = "")
```

## Higher initial value of K

Steady state is achieved faster. 

```{r}
solow$variables[5, 2]=2 # changing initial value of k
solow<-sfc.check(solow,fill=T)
data1<-simulate(solow, maxIter=200)
y_model2=data1$baseline[,"y"]

plot(y_model2, t="l", ylab="ouput per worker", xlab = "") 
lines(y_model1, t="l", col="blue", xlab="")
```

## Permanent increase in savings rate from 20% to 40%, after 100 iterations

We see that the model already had achieved steady state, but that the increase in the savings rate by 20%-points, made output pr. worker accelerate a lot until the new steady state is achieved. This happens as more money flows into investment in capital. 
```{r}
# I create a shock after 100 iterations
init = data$baseline[0,]
shock1<-sfc.addScenario(model=solow,vars="s",values=0.4,inits=100,ends=200,starts=init) 
shock1_data<-simulate(shock1, maxIter=200)
y_shock1<-shock1_data$scenario[,"y"]

par(mar=c(2,2,2,2))
plot(y_shock1, t="l", ylab="ouput per worker", xlab = "")
```

We can now plot the effect on the growth rate of output pr. worker. (GDP rate). 

We see that when the shock hits at iteration 100 the growth ratee spikes, whereafter it deaccelerate until it hits 0 in steady state. 
```{r}
# Plot the results of savings rate shock on growth rate of output per worker
growth_model2=diff(log(y_model2))
growth_shock1=diff(log(y_shock1))
plot(growth_shock1, t="l", ylab="growth rate of y", xlab = "") 
lines(growth_model2, t="l", col="blue", xlab="")
```






